Continuous Generalization of Buildings by Growing and Merging

### 2017-09-06 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
made our program run faster

The area of a building on map should be at least $a\,\mathrm{mm}^2$ so that 
the 
building is large enough to be perceived.
In \sect\ref{sec:Simplify}, we show that we set $a=4$.
Accordingly, a square at the start map should have 
area $a M_\mathrm{s}^2\,\mathrm{mm}^2$ at least, and
a square at the goal map should have 
area $a M_\mathrm{g}^2\,\mathrm{mm}^2$ at least.
The difference of the side lengths is 
$\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm}$ 
(see \fig\ref{fig:Growth}).
A square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
(M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm}$ so that 
it can survive when users zoom out from 
the start map to the goal map.
In order to eliminate small buildings, 
we define our growing distance as
\begin{equation}
\label{eq:d_G}
d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} 
(M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm} 
\quad 0 < \lambda <1,
\end{equation}
where variable $\lambda$ is a growing factor. 
A larger $\lambda$ results in  
fewer buildings to be eliminated, and vice versa.
During our growing, the growth at time $t$ is
\begin{equation}
\label{eq:d_Gt}
\dtrm{G} = t \cdot d_\mathrm{G}.
\end{equation}

\begin{figure*}[tb]
	\centering
	\includegraphics{Growth}
	\caption{Growth.}
	\label{fig:Growth}
\end{figure*}

@@

\subsection{Unite buildings of the immediately previous step}
\label{sec:Unite}

@@

@@

\subsection{Merge close buildings by introducing bridges}
The distance between two buildings on a map should be larger than a threshold
\citep{Regnauld2001,Li2004}.
Following \citet{Basaraner2008,Stoter2009}, 
we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$. 
The real separation distance at time $t$ is
\begin{equation}
\label{eq:d_epsilont}
d_{\epsilon, t} = \epsilon \cdot M_t.
\end{equation}

For each pair of buildings in the same group, 
we find the smallest distance between them.
We connect the buildings by adding an edge from the nearest points.
We find a minimum spanning tree of the buildings using Prim's algorithm 
\citep{Prim1957}.
We enlarge and merge buildings as the way we do in \sect\ref{sec:Grouping}.

\subsection{Group buildings based on buffering}
\label{sec:Grouping}
We group buildings based on the buffers of the buildings 
(see \fig\ref{fig:RemoveBay} for example). 
We buffer each building with distance $\dtrm{G} + d_{\epsilon,t}/2$
(see \eqs\ref{eq:d_Gt} and~\ref{eq:d_epsilont}).
We grow an additional $d_{\epsilon,t}/2$ so that if two buffers overlap, 
the corresponding two buildings will become too close at time $t$.
As a result, the two buildings are identified as in the same group.

We merge the buffers which overlap each others so that we have some large 
units.
Now we iteratively remove small ``bays''.
Each iteration consists of three steps, i.e., 
buffering with distance $r_H$, buffering with distance $-r_H$, and
merging overlapping units.
The iterative process stops when the number of units do not decrease anymore.

All the buildings overlapping with the same unit belong to the same group.

\begin{figure*}[tb]
	\centering
	\includegraphics[draft=false]{RemoveBay}
	\caption{Group buildings iteratively.
		(a) Original buildings.
		(b) Dilate each building in (a) with distance $\dtrm{G}+\dtrm{D}$.		
		(c) Erode the polygons in (b) with distance $\dtrm{D}$.
		(d) Dilate the polygons in (c) with distance 
		$\frac{\sqrt{5}}{2} d_{\epsilon,t}$. 
		If two polygons in (d) intersect, 
		the original buildings in (a) will be put in the same group 
		because they will become too close at time $t$.
		Until this step, there two groups according to (d), 
		one consists of the single middle building and 
		the other group consists of the surrounding $9$ buildings.
		The process of (e), (f), and (g) is similar to 
		that of (b), (c), and (d).		
		The difference is that 
		instead of applying the operators to each single building, 
		we do that for the buildings in the same group.
		There is only one group left according to (g).
		We iteratively group buildings in this way until the number of groups 
		does not decrease.
	}
	\label{fig:RemoveBay}
\end{figure*}

\subsection{Generate buildings on goal map}
\label{sec:Goal}
We group

@@

\subsection{Parameters for growing and simplifying}

If we insist on that we should observe 
the growing, say, $x \% (0<x<100)$ of the time at least, then we should make 
sure that
\begin{equation}
\label{eq:a_limit}
\frac{d_\mathrm{G}}{d_\mathrm{G}+d_\epsilon} \ge x \%.
\end{equation}
Using $d_\mathrm{G}$ and $d_\epsilon$ from Eqs.~\ref{eq:d_G} 
and~\ref{eq:d_epsilon}, we transform Eq.~\ref{eq:a_limit} to
\begin{equation}
a \ge \Big(\frac{2 \epsilon S_g x}{\lambda (100-x) (S_g-S_s)}\Big)^2
\end{equation}
We also require 
that $S_g \ge 2 S_s$, which means $S_s \le \frac{1}{2} S_g$.
On one hand, we should have a large $x$ so that we will see the 
growing most of the time.
On the other hand, we wish to keep bridges short as bridges are intrusions to 
our map, which means we should have a small $x$ and a large $\lambda$ so that 
we will have a small 
$a$ (according to Eq.~\ref{eq:a_limit}), a small $d_\mathrm{G}$ (according to 
Eq.~\ref{eq:d_G}), and finally a small $l_b$ (according to 
Eq.~\ref{eq:BridgeLength}). Also we should have a small $x$ and a large 
$\lambda$ as our $a$ is already much larger than $0.16\,\mathrm{mm}^2$ on 
map, which is the area limit used by \citet{Stoter2009}. As a result, we 
set 
$\lambda=0.8$ and $x=\frac{2}{3} \cdot 100$.
Using these setting, we have
\begin{equation}
a \ge 4.
\end{equation}
according to Eq.~\ref{eq:a_limit}.

Therefore, we may grow up to distance 
\[
D_\mathrm{G} = d_\mathrm{G} + d_\epsilon.
\]
Fig.~\ref{fig:ExtraGrowth} shows such an enlargement and simplification, 
where  
variable $d_\mathrm{e} (\le d_\epsilon)$ is the extra growing distance.

\citet{Chaudhry2008} thought that a hole of a settlement should be at least 
$0.5\,\mathrm{km}^2$ for a map at scale $1:250{,}000$, 
which means that the hole is at least $8\,\mathrm{mm}^2$ on map. 
Following their setting, we shrink a hole and 
eliminate the hole once its size is smaller than $8\,\mathrm{mm}^2$ on map.

@@

\begin{figure*}[tb]
	\centering
	\includegraphics{ExtraGrowth}
	\caption{In the left figure, the green polygon represents a building, and 
		the gray polygon is the enlargement of the building. In the right 
		figure, the gray polygon has been simplified to a rectangle. In order 
to 
		fill the rectangle, most parts of the (green) building needs to grow 
with
		distance $d_\mathrm{G}$, but the pit needs to grow with $d_G + 
		d_\mathrm{e}$, 
		where $d_\mathrm{e}$ is the extra growing distance.}
	\label{fig:ExtraGrowth}
\end{figure*}

\begin{figure*}[tb]
	\centering
	\includegraphics{GrowingExample}
	\caption{GrowingExample.}
	\label{fig:GrowingExample}
\end{figure*}

\subsection{Running time analysis}
Although a version with a 
lower running time exists \citep[see][]{Chan1992}, we implemented the basic 
version.

@@

@@

To make it more efficient for on line displaying, we may need 
some external memories. First, we store the data at some key 
scales so that we may start a generalization from the immediate 
larger scale; $O(n)$ space. Second, we store the target shape 
for each building; $O(n)$ space. Third, we store the aggregation 
time and the target form for the aggregated shape; $O(n^2)$ 
space if we count vertex number.
%
The displaying time is dependent on buffering and clipping.

We our intermediate results may violate more cartographic rules, but we try to 
make the results at goal scales violate as few rules as possible.

>>>>

%The area of a building on map should be at least $a\,\mathrm{mm}^2$ so that 
%the 
%building is large enough to be perceived.
%In \sect\ref{sec:Simplify}, we show that we set $a=4$.
%Accordingly, a square at the start map should have 
%area $a M_\mathrm{s}^2\,\mathrm{mm}^2$ at least, and
%a square at the goal map should have 
%area $a M_\mathrm{g}^2\,\mathrm{mm}^2$ at least.
%The difference of the side lengths is 
%$\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm}$ 
%(see \fig\ref{fig:Growth}).
%A square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
%(M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm}$ so that 
%it can survive when users zoom out from 
%the start map to the goal map.
%In order to eliminate small buildings, 
%we define our growing distance as
%\begin{equation}
%\label{eq:d_G}
%d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} 
%(M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm} 
%\quad 0 < \lambda <1,
%\end{equation}
%where variable $\lambda$ is a growing factor. 
%A larger $\lambda$ results in  
%fewer buildings to be eliminated, and vice versa.
%During our growing, the growth at time $t$ is
%\begin{equation}
%\label{eq:d_Gt}
%\dtrm{G} = t \cdot d_\mathrm{G}.
%\end{equation}
%
%\begin{figure*}[tb]
%	\centering
%	\includegraphics{Growth}
%	\caption{Growth.}
%	\label{fig:Growth}
%\end{figure*}

We denote by $d_\mathrm{G}$ the total growth. The growth at time $t$ is
\begin{equation}
\label{eq:d_Gt}
\dtrm{G} = t \cdot d_\mathrm{G}.
\end{equation}

@@

\subsection{Group buildings based on buffering}
\label{sec:Group}
We group buildings based on their buffers
(see \fig\ref{fig:RemoveBay} for example).
We wish to remove some ``bays'' 
which have widths less than $2 \dtrm{D}$.
A bay may appear after some buildings are merged by bridging
(see for example \fig\ref{fig:RemoveBay}e).
To remove a such kind of bay,
we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 
and then erode back (see \fig\ref{fig:RemoveBay}c and~f) 
with distance $\dtrm{D}$.
There may be some buildings in a bay (see \fig\ref{fig:RemoveBay}c),
so we iteratively group until the number of groups does not decrease.
The result of having removed a bay is the outer polygon of 
\fig\ref{fig:RemoveBay}h. 
In comparison, the result is \fig\ref{fig:RemoveBay}e 
if we do not remove a bay.
Note that the pit we want to remove in \fig\ref{fig:RemovePitAndSpike} is a 
kind of bay and will be removed by overgrowing.

\begin{figure*}[tb]
	\centering
	\includegraphics[draft=false]{RemoveBay}
	\caption{Group buildings iteratively.
		(a) Original buildings.
		(b) Dilate each building in (a) with distance $\dtrm{G}+\dtrm{D}$.		
		(c) Erode the polygons in (b) with distance $\dtrm{D}$.
		(d) Dilate the polygons in (c) with distance 
		$\frac{\sqrt{5}}{2} d_{\epsilon,t}$. 
		If two polygons in (d) intersect, 
		the original buildings in (a) will be put in the same group 
		because they will become too close at time $t$.
		Until this step, there two groups according to (d), 
		one consists of the single middle building and 
		the other group consists of the surrounding $9$ buildings.
		(e) The result of growing and merging at time $t$ 
		if we use $\dtrm{D}=0$.
		The process of (f), (g), and (h) is similar to 
		that of (b), (c), and (d).		
		The difference is that 
		instead of applying the operators to each single building, 
		we do that for the buildings in the same group.
		In (f), we manage to remove the bay in (e) by additionally dilating 
		with distance $\dtrm{D}$.
		There is only one group left according to (h).
		We iteratively group buildings in this way until the number of groups 
		does not decrease.
	}
	%in this example, we used _dblTotalGrow *= 5;
	\label{fig:RemoveBay}
\end{figure*}

\subsection{Merge close buildings by introducing bridges}
\label{sec:Merge}
The distance between two buildings on a map should be larger than a threshold
\citep{Regnauld2001,Li2004}.
Following \citet{Basaraner2008,Stoter2009}, 
we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$. 
The real separation distance at time $t$ is
\begin{equation}
\label{eq:d_epsilont}
d_{\epsilon, t} = \epsilon \cdot M_t.
\end{equation}

For each pair of buildings in the same group, 
we find the smallest distance between them.
We connect the buildings by adding an edge from the nearest points.
We find a minimum spanning tree of the buildings using Prim's algorithm 
\citep{Prim1957}.
We enlarge and merge buildings as the way we do in \sect\ref{sec:Group}.

\subsection{Generate the goal forms of buildings}
\label{sec:Goal}
To generate the goal forms of buildings, we set time $t=1$.
We group (see \sect\ref{sec:Group}) 
and merge (see \sect\ref{sec:Merge}) buildings on start map.
Then we grow (see \sect\ref{sec:Grow}) 
and simplify (see \sect\ref{sec:Simplify}) the merged buildings.
See for example \fig\ref{fig:Buffer_MiterLimits}, 
the building at time $t=1$ is the goal form of the three buildings of $t=0$.

\subsection{Generate buildings on intermediate maps}
\label{sec:Unite}

@@

A building on an intermediate map should never exceed
the goal form of the group of buildings 
which include the united buildings. 
Otherwise, the building will need to be shrunk.
To guarantee the non-exceeding, 
we clip the building by the goal form 
and remove the parts outside.
\todo{example?}

@@

@@

%\subsection{Parameters for growing and simplifying}
%
%
%
%
%If we insist on that we should observe 
%the growing, say, $x \% (0<x<100)$ of the time at least, then we should make 
%sure that
%\begin{equation}
%\label{eq:a_limit}
%\frac{d_\mathrm{G}}{d_\mathrm{G}+d_\epsilon} \ge x \%.
%\end{equation}
%Using $d_\mathrm{G}$ and $d_\epsilon$ from Eqs.~\ref{eq:d_G} 
%and~\ref{eq:d_epsilon}, we transform Eq.~\ref{eq:a_limit} to
%\begin{equation}
%a \ge \Big(\frac{2 \epsilon S_g x}{\lambda (100-x) (S_g-S_s)}\Big)^2
%\end{equation}
%We also require 
%that $S_g \ge 2 S_s$, which means $S_s \le \frac{1}{2} S_g$.
%On one hand, we should have a large $x$ so that we will see the 
%growing most of the time.
%On the other hand, we wish to keep bridges short as bridges are intrusions to 
%our map, which means we should have a small $x$ and a large $\lambda$ so that 
%we will have a small 
%$a$ (according to Eq.~\ref{eq:a_limit}), a small $d_\mathrm{G}$ (according to 
%Eq.~\ref{eq:d_G}), and finally a small $l_b$ (according to 
%Eq.~\ref{eq:BridgeLength}). Also we should have a small $x$ and a large 
%$\lambda$ as our $a$ is already much larger than $0.16\,\mathrm{mm}^2$ on 
%map, which is the area limit used by \citet{Stoter2009}. As a result, we 
%set 
%$\lambda=0.8$ and $x=\frac{2}{3} \cdot 100$.
%Using these setting, we have
%\begin{equation}
%a \ge 4.
%\end{equation}
%according to Eq.~\ref{eq:a_limit}.
%
%
%
%
%Therefore, we may grow up to distance 
%\[
%D_\mathrm{G} = d_\mathrm{G} + d_\epsilon.
%\]
%Fig.~\ref{fig:ExtraGrowth} shows such an enlargement and simplification, 
%where  
%variable $d_\mathrm{e} (\le d_\epsilon)$ is the extra growing distance.
%
%
%\citet{Chaudhry2008} thought that a hole of a settlement should be at least 
%$0.5\,\mathrm{km}^2$ for a map at scale $1:250{,}000$, 
%which means that the hole is at least $8\,\mathrm{mm}^2$ on map. 
%Following their setting, we shrink a hole and 
%eliminate the hole once its size is smaller than $8\,\mathrm{mm}^2$ on map.

@@

%\begin{figure*}[tb]
%	\centering
%	\includegraphics{ExtraGrowth}
%	\caption{In the left figure, the green polygon represents a building, and 
%		the gray polygon is the enlargement of the building. In the right 
%		figure, the gray polygon has been simplified to a rectangle. In order 
%to 
%		fill the rectangle, most parts of the (green) building needs to grow 
%with
%		distance $d_\mathrm{G}$, but the pit needs to grow with $d_G + 
%		d_\mathrm{e}$, 
%		where $d_\mathrm{e}$ is the extra growing distance.}
%	\label{fig:ExtraGrowth}
%\end{figure*}

%\begin{figure*}[tb]
%	\centering
%	\includegraphics{GrowingExample}
%	\caption{GrowingExample.}
%	\label{fig:GrowingExample}
%\end{figure*}

%\subsection{Running time analysis}
%Although a version with a 
%lower running time exists \citep[see][]{Chan1992}, we implemented the basic 
%version.

@@

%Although a version with a 
%lower running time exists \citep[see][]{Chan1992}, we implemented the basic 
%version

@@

Our intermediate results may violate more cartographic rules, but we try to 
make the results at goal scales violate as few rules as possible.
